Self Regulation Ontology Retest Analyses

### 2018-05-16 code/SRO_Retest_Analyses.Rmd
frisem practice

```{r}
boot_df %>%
  select(dv, p_time, task) %>%
  mutate(time_effect_sig = ifelse(p_time<0.05,1,0)) %>%
  group_by(dv)%>%
  summarise(pct_sig_time_effect = sum(time_effect_sig)/10,
            task = unique(task))%>%
  filter(pct_sig_time_effect>5) %>%
  arrange(task,-pct_sig_time_effect) %>%
  ungroup()%>%
  group_by(task) %>%
  summarise(count=n()) %>%
  mutate(total_num_vars = c(74, 372),
         prop = count/total_num_vars) %>%
  ggplot(aes(task, prop, fill=task))+
  geom_bar(stat="identity", alpha=0.5, width=0.5)+
  theme(legend.position = "none", 
        axis.text.x = element_text(size=14),
        axis.title.y = element_text(size=14))+
  ylab("Proportiono of samples")+
  xlab("")+
  ylim(0,1)

@@

mean_diff_df %>%
  left_join(valence_df, by = c("dv", "task")) %>%
  mutate(sc_increase = ifelse(prop_one_direction>0&valence==1,1,ifelse(prop_one_direction<0&valence==-1,1,0)),
         sc_decrease = ifelse(prop_one_direction>0&valence==-1,1,ifelse(prop_one_direction<0&valence==1,1,0))) %>%
  group_by(task) %>%
summarise(sum_sc_increase = sum(sc_increase,na.rm=T),
          sum_sc_decrease = sum(sc_decrease,na.rm=T)) %>%
  gather(key, value, -task) %>%
  mutate(total_vars = c(74, 372, 74, 372),
         prop = value/total_vars) %>%
  ggplot(aes(key, prop, group=task, fill=task))+
  geom_bar(stat = "identity", position = position_dodge(), alpha = 0.5)+
  theme(legend.title = element_blank(),
        axis.title.y = element_text(size=14),
        axis.text.x = element_text(size=14))+
  xlab("")+
  ylab("Proportion")+
  ylim(0, 1)+
  scale_x_discrete(breaks = c("sum_sc_decrease", "sum_sc_increase"),
                   labels = c("Self-control decrease", "Self-control increase"))

>>>>

```{r}
boot_df %>%
  select(dv, p_time, task) %>%
  mutate(time_effect_sig = ifelse(p_time<0.05,1,0)) %>%
  group_by(dv)%>%
  summarise(pct_sig_time_effect = sum(time_effect_sig)/10,
            task = unique(task))%>%
  filter(pct_sig_time_effect>5) %>%
  arrange(task,-pct_sig_time_effect) %>%
  ungroup()%>%
  group_by(task) %>%
  summarise(count=n()) %>%
  mutate(total_num_vars = c(74, 372),
         prop = count/total_num_vars) %>%
  ggplot(aes(task, prop, fill=task))+
  geom_bar(stat="identity", alpha=0.5, width=0.5)+
  theme(legend.position = "none", 
        axis.text.x = element_text(size=14),
        axis.title.y = element_text(size=14))+
  ylab("Proportiono of bootstrap samples")+
  xlab("")+
  ylim(0,1)

@@

mean_diff_df %>%
  left_join(valence_df, by = c("dv", "task")) %>%
  mutate(sc_increase = ifelse(prop_one_direction>0&valence==1,1,ifelse(prop_one_direction<0&valence==-1,1,0)),
         sc_decrease = ifelse(prop_one_direction>0&valence==-1,1,ifelse(prop_one_direction<0&valence==1,1,0))) %>%
  group_by(task) %>%
summarise(sum_sc_increase = sum(sc_increase,na.rm=T),
          sum_sc_decrease = sum(sc_decrease,na.rm=T)) %>%
  gather(key, value, -task) %>%
  mutate(total_vars = c(74, 372, 74, 372),
         prop = value/total_vars) %>%
  ggplot(aes(key, prop, group=task, fill=task))+
  geom_bar(stat = "identity", position = position_dodge(), alpha = 0.5)+
  theme(legend.title = element_blank(),
        axis.title.y = element_text(size=14),
        axis.text.x = element_text(size=14))+
  xlab("")+
  ylab("Proportion of measures")+
  ylim(0, 1)+
  scale_x_discrete(breaks = c("sum_sc_decrease", "sum_sc_increase"),
                   labels = c("Self-control decrease", "Self-control increase"))
